The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
acknowledgements - add WG reviewers for ALR submissions

We thank all members of the Wildlife Evolutionary Ecology Lab, including XXXXX **check WG reviewers** for their comments on previous versions of this manuscript as well as D. Schneider for inspiration and helpful discussions about scale. Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.

>>>>

We thank all members of the Wildlife Evolutionary Ecology Lab, including K. Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, and L. Newediuk for their comments on previous versions of this manuscript as well as D. Schneider for inspiration and helpful discussions about scale. Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.
